\documentclass[11pt,a4paper,sans]{moderncv}

% Style and color options
\moderncvstyle{banking} % Style options: casual, classic, banking, etc.
\moderncvcolor{blue}    % Color options: blue, orange, green, etc.

% Adjust margins
\usepackage[scale=0.85]{geometry}

% Personal data
\name{Junseo}{Min}
\title{Researcher} % Optional
\email{minjs4562@gmail.com}
\social[github]{JunseoMin}
\social[linkedin]{junseo-min-b638582bb}

% Begin document
\begin{document}

% Header
\makecvtitle

% Personal statement
\section{Personal Statement}
Every moment adds to my value; my worth increases with every passing moment. \\
My deep interest lies in SLAM, navigation, and deep learning. My ultimate dream is to one day tell my children that I developed the algorithm used in a car or a robot.

% Education
\section{Education}
\cventry{Major}{Robotics}{Kwangwoon University}{}{}{}
\cventry{Minor}{Computer Science}{Kwangwoon University}{}{}{}

% Contact & URLs
\section{Contact \& URLs}
\cvitem{Email}{\emaillink{minjs4562@gmail.com}}
\cvitem{GitHub}{\httplink{https://github.com/JunseoMin}}
\cvitem{LinkedIn}{\httplink{https://www.linkedin.com/in/junseo-min-b638582bb/}}
\cvitem{Blog (Korean)}{\httplink{https://velog.io/@junseomin/posts}}
\cvitem{Portfolio}{\href{https://dawn-blob-54d.notion.site/JunseoMin-Autonomous-driving-SW-developer-aba4766e42184bc680a5f4363c4f2c3a}{Junseo's Portfolio}}



% Experience
\section{Career}

\cventry{2022.6--2024.09}{2022 Samsung Unpack Project - Web QA}{Cheil Worldwide}{Seoul, South Korea}{}{
\begin{itemize}
    \item Conducted QA for product description pages and collaborated with overseas teams.
    \item Developed an interest in software development, leading to a Computer Science minor.
\end{itemize}}

\cventry{2022.12--2023.12}{Undergraduate Research Assistant}{Ubiquitous \& AI Lab}{Seoul, South Korea}{}{
\begin{itemize}
    \item Studied machine learning fundamentals and transformer attention modules through research papers and advisor discussions.
    \item Developed a stock price prediction model for the KRX competition using TensorFlow and advanced deep learning techniques.
\end{itemize}}

\cventry{2023.12--2024.09}{Autonomous Driving Developer}{Immersion}{Seoul, South Korea}{}{
\begin{itemize}
    \item Built outdoor HD maps and implemented SLAM pipelines for autonomous robots using 3D LiDAR and ROS2.
    \item Solved technical challenges like sunlight interference and resource limits on Jetson Orin.
\end{itemize}}

\cventry{2024.06--Present}{Research Intern}{Machine Perception and Intelligence Lab (GIST)}{Gwangju, South Korea}{}{
\begin{itemize}
    \item Designed LiDAR reconstruction models using Point Transformer V3 and Perceiver architectures.
    \item Conducted research on localization-related models and advanced 3D reconstruction techniques
\end{itemize}}

% Activities
\section{Activities}
\cventry{2020.03--2020.11}{Academic Research Club}{Kwangwoon University}{Baram}{}{}
\cventry{2020.03--2020.11}{Student Council}{Kwangwoon University}{Robotics Department}{}{}
\cventry{2023.05--2023.10}{Autonomous Driving Technician Training Program}{Kwangwoon University}{}{}{}


% Projects
\section{Projects}
\cvitem{1. HD Map Implementation}{Developed a high-definition map for advertising robots using ROS and FAST-LIO2. Researched sunlight interference solutions.}
\cvitem{2. Attention Robot Implementation}{Implemented Stanley controller, path planning, and NDT-OMP localization in ROS2, optimizing performance with OpenMP and Eigen.}
\cvitem{3. Stock Prediction Model}{Built a Transformer-based stock prediction model using KOSPI data.}
\cvitem{4. SmartFarm worker assistant Robot} {Developed end-to-end system for mushroom harvesting robot.}

\section{Articles}
\cvitem{}{\textbf{Junseo Min}, Inseok Jeon, Sumin Lee, Yunkyo Hong, "AI-Based Worker Assistant Robot: Shaping the Future of Smart Farms", ICROS 2023}

\section{Skills \& Interests}
\cvitemwithcomment{Programming}{C++, Python, ROS1/2, PyTorch}{Strong}
\cvitemwithcomment{Knowledge}{Java, Serial Data, Computer Vision}{Intermediate}
\cvitemwithcomment{Interest}{SLAM, Navigation, Localization}{Professional Interests}

\end{document}
